### 2019-12-20 paper/introduction.tex
After Andrei's comments in Model Description #6

Boron carbide (B$_4$C) is commonly used material for the control rods 
\cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}. 
However, we may need to enrich the boron isotope ($^{10}$B) to reach 
the necessary absorption cross section. Additionally, issues related to helium gas release, swelling,
and high loss of the reactivity worth limit the B$_4$C lifespan 
\cite{guo2019optimized}. Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 
potential alternative absorbers for Generation-IV reactors such as 
hafnium-based materials and rare earth element oxides. These absorbers have 
high thermal conductivity, good resistance to neutron irradiation, and release 
almost no gas 
\cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.

>>>>

Boron carbide (B$_4$C) is commonly used material for the control rods 
\cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}. 
However, we may need to enrich the boron isotope ($^{10}$B) to reach 
the necessary absorption cross section. Additionally, issues related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, swelling,
and high loss of the reactivity worth limit the B$_4$C lifespan 
\cite{guo2019optimized}. Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 
potential alternative absorbers for Generation-IV reactors such as 
hafnium-based materials and rare earth element oxides. These absorbers have 
high thermal conductivity, good resistance to neutron irradiation, and release 
almost no gas (absorbing neutrons mainly through (n,$\gamma$) reactions)
\cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.

### 2019-12-20 paper/methods.tex
After Andrei's comments in Model Description #6

In this study, the fuel salt composition is 70LiF - 17.5BeF$_2$ - 
12.5(HM)F$_N$ mole\%, where HM is the heavy metal (i.e. $^{232}$Th and fissile 
materials), and $N$ depends on the chosen fissile material and the  
thermochemical state of the liquid fuel salt. Three different types of initial 
fissile materials are considered: (1) $^{233}$U \cite{ashraf2019whole_core}, 
(2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
respectively. The liquid fuel salt circulates continuously through the fuel 
tubes that pierce the graphite hexagonal prisms. The core is surrounded by 
axial and radial graphite reflectors to minimize the neutron leakage. Finally, 
the \gls{SD-TMSR} pressure vessel holds all reactor components and is made of 
a Hastelloy N alloy. The main characteristics of the \gls{SD-TMSR} are 
summarized in Table~\ref{tab:table1}.

@@

The reactivity of the SD-TMSR core is controlled by two clusters of control 
rods:
\begin{enumerate}
\item Control Safety Devices (CSD);
\item Shutdown Safety Devices (SSD).
\end{enumerate}
The CSD system is designed for reactivity control during normal operation and the SSD system is designed for an emergency reactor shutdown.
In the present work, five different absorbing materials are considered based on their neutronics and safety performance:
\begin{enumerate}
\item B$_4$C with boron enriched to 90\% $^{10}$B;
\item hafnium diboride (HfB$_2$);
\item hafnium hydride (HfH$_{1.62}$);
\item gadolinium oxide (Gd$_2$O$_3$);
\item europium oxide (Eu$_2$O$_3$).
\end{enumerate}
Boron carbide (B$_4$C) is widely used in control rods fabrication. Enriching 
PB$_4$C increases the fraction of highly neutron absorber isotope (i.e. 
$^{10}$B) and helps to reach the necessary absorptivity. However, issues 
related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, 
swelling, melting risk, and high loss of the reactivity worth limit the B$_4$C 
lifespan \cite{guo2019optimized}. Hafnium and rare earth elements oxides 
absorb neutrons through (n,$\gamma$) reactions and this limits gas emission.

The control rod is a cylinder with a radius of 0.75 cm and a height of 520 cm. 
The absorbing material is surrounded by a 0.25-cm-thick cladding made of AIM1 
(15Cr-15Ni) steel alloy \cite{SERAN2017285} and the rod follower is made of 
SiC structural material (see Figure~\ref{fig:cr}). A small gap between the 
cladding and rod follower is considered to facilitate the control rod movement.

@@

Figure~\ref{fig:core_25} illustrates the numbering scheme of control rods 
clusters in the SD-TMSR core.
The CSD1-16 clusters are represented as yellow color and distributed as two rings: inner and outer ring (peripheral ring). The inner ring includes CSD from 1 to 6, while the outer ring includes CSD from 7 to 16. Red color stands for SSD1-9 clusters.
We distributed the graphite elements with control rods clusters uniformly in 
the inner core of the SD-TMSR, where the moderator-to-fuel ratio is high.
The selected core segment at the upper left corner of the 
Figure~\ref{fig:core_25} shows that both CSD and SSD clusters consist of four 
control rods located at the same distance from the fuel channel center.
\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{core_25.png}
	\caption{Distribution of the graphite elements with control rods in the SD-TMSR core.}
	\label{fig:core_25}
\end{figure}

\section{Methodology and tools} \label{Methodology-and-tools}
\subsection{Control rod design evaluation}
In this work, SERPENT-2 version 2.1.31 \cite{leppanen2014serpent} is used to 
perform steady state calculations for the full-core of the SD-TMSR with 
suggested control rod design. We adopted the ENDF-VII.0 cross section library 
for all calculations in the present work. The results demonstrate whole-core 
runs of $12.5\times 10^6$ neutron histories per depletion step. The 
statistical error in $k_{eff}$ from SERPENT-2 output is equal to $\pm$ $25$ 
$pcm$.

@@

\begin{figure}[t!] % replace 't' with 'b' to \centering
	\centering
	\includegraphics[width=\textwidth]{core_26.png}
	\caption{$XZ$ section of the full-core model of the SD-TMSR, CRs are fully withdrawn.}
	\label{fig:core_26}
\end{figure}

@@

Equation~\ref{Equ:5} is used to calculate the differential CRW [\$/cm], where 
$\Delta H$ is the height change of control rod [cm] before and after 
insertions.

\begin{equation}
\label{Equ:5}
\dfrac{{\partial}{\rho}_{i}}{{\partial{H}}}=\dfrac{1}{{\Delta}{H}}\dfrac{{k_{i}}-{k_{i-1}}}{{{k_{i}}{k_{i-1}}}{{\beta}_{i}}},
\end{equation}

>>>>

In this study, the fuel salt composition is 70LiF - 17.5BeF$_2$ - 
12.5(HM)F$_N$ mole\%, where HM is the heavy metal (i.e. $^{232}$Th and fissile 
materials), and $N$ depends on the chosen fissile material and the  
thermochemical state of the liquid fuel salt. Three different types of initial 
fissile materials are considered: (1) $^{233}$U \cite{ashraf2019whole_core}, 
(2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
respectively. The liquid fuel salt circulates continuously through the fuel 
tubes that pierce the graphite hexagonal prisms. The core is surrounded by 
axial and radial graphite reflectors to minimize the neutron leakage.
A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
Finally, the \gls{SD-TMSR} pressure vessel holds all reactor components and is made of 
a Hastelloy N alloy. The main characteristics of the \gls{SD-TMSR} are 
summarized in Table~\ref{tab:table1}.

@@

The reactivity of the SD-TMSR core is controlled by two clusters of control 
rods:
\begin{enumerate}
\item Control Safety Devices (CSD);
\item Shutdown Safety Devices (SSD).
\end{enumerate}
The CSD system is designed for reactivity control during normal operation and the SSD system is designed for an emergency reactor shutdown.
In the present work, five different absorbing materials are considered based on their neutronics and safety performance:
\begin{enumerate}
\item B$_4$C with boron enriched to 90\% $^{10}$B;
\item hafnium diboride (HfB$_2$);
\item hafnium hydride (HfH$_{1.62}$);
\item gadolinium oxide (Gd$_2$O$_3$);
\item europium oxide (Eu$_2$O$_3$).
\end{enumerate}

The control rod is a cylinder with a radius of 0.75 cm and a height of 520 cm. 
The absorbing material is surrounded by a 0.25-cm-thick cladding made of AIM1 
(15Cr-15Ni) steel alloy \cite{SERAN2017285} and the guide tube is made of 
SiC structural material (see Figure~\ref{fig:cr}). We simulated a small gap between the 
cladding and guide tube to facilitate the control rod movement.

@@

Figure~\ref{fig:core_25} illustrates the numbering scheme of control rods 
clusters in the SD-TMSR core.
The CSD1-16 clusters are represented as yellow color and distributed as two rings: inner and outer ring (peripheral ring). The inner ring includes CSD from 1 to 6, while the outer ring includes CSD from 7 to 16. Red color stands for SSD1-9 clusters.
We distributed the graphite elements with control rods clusters uniformly in 
the inner core of the SD-TMSR, where the moderator-to-fuel ratio is high.
The selected core segment at the upper left corner of the 
Figure~\ref{fig:core_25} shows that both CSD and SSD clusters consist of four 
control rods located at the same distance from the fuel channel center.
\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{core_25.png}
	\caption{Distribution of the graphite elements with control rods in the SD-TMSR core. Green - fuel salt, blue - graphite, pink - B$_4$C, and light-green - vessel (H-alloy).}
	\label{fig:core_25}
\end{figure}

\section{Methodology and tools} \label{Methodology-and-tools}
\subsection{Control rod design evaluation}
In this work, SERPENT-2 version 2.1.31 \cite{leppanen2014serpent} is used to 
perform steady state calculations for the full-core of the SD-TMSR with 
suggested control rod design. We adopted the ENDF-VII.0 cross section library 
for all calculations in the present work. The results demonstrate whole-core 
runs of $50,000$ neutrons per cycle, for 50 inactive and 500 active cycles. The 
statistical error in $k_{eff}$ from SERPENT-2 output is $\leq$ $25$ 
$pcm$.

@@

\begin{figure}[t!] % replace 't' with 'b' to \centering
	\centering
	\includegraphics[width=\textwidth]{core_26.png}
	\caption{$XZ$ view at the midplane of the full-core model of the SD-TMSR, 10 CRs are fully withdrawn.}
	\label{fig:core_26}
\end{figure}

@@

Equation~\ref{Equ:5} is used to calculate the differential CRW [\$/cm], where 
$Z$ is the coordinate of the bottom of the control rod.

\begin{equation}
\label{Equ:5}
\dfrac{{\partial}{\rho}_{i}}{{\partial{Z}}}=\dfrac{1}{{\Delta}{Z}}\dfrac{{k_{i}}-{k_{i-1}}}{{{k_{i}}{k_{i-1}}}{{\beta}_{i}}},
\end{equation}
